Behavior Driven Development in Haskell

### 2012-05-25 paper.tex
going without Hspec credit.

\authorinfo{Simon HENGEL}
           {TBD: Affiliation}
           {TBD: Email}
\authorinfo{Trystan SPANGLER}
           {TBD: Affiliation}
           {TBD: Email}
\authorinfo{Kazuhiko YAMAMOTO}
           {IIJ Innovation Institute Inc.}
           {kazu@iij.ad.jp}

@@

In this paper, we explore how to apply BDD to Haskell.
We brought BDD methods from other programming language communities and
integrated them with a Haskell-original test method.
In particular, we introduced {\tt doctest}~\cite{doctest} and
integrated with QuickCheck~\cite{quickcheck}.
We also implemented {\tt Hspec} inspired by rspec~\cite{rspec}
and integrated with QuickCheck.

@@

\begin{itemize}
\item Introduced {\tt doctest} from Python community to Haskell community
and integrated it with QuickCheck
(Section \ref{sec:Visible-behavior} and Section \ref{sec:doctest})
\item Introduced {\tt Hspec} from Ruby community to Haskell community and
integrated it with QuickCheck
(Section \ref{sec:Internal-behavior} and Section \ref{sec:hspec})
\item Show best current practice of behavior driven development in Haskell (Section \ref{ref:Best-current-practice})
\end{itemize}

@@

In Haskell community, HUnit and QuickCheck are commonly used %% what about SmallCheck?
and the {\tt test-framework} package integrates them.
We can categorize the {\tt test-framework} package into
a tool of TDD.
Before our work, there is no BDD tool commonly used in Haskell community.

@@

To specify visible behavior, we propose to add two new annotation syntax to Haddock and to use {\tt doctest} integrated with QuickCheck. To describe internal behavior, we propose to use {\tt Hspec} aslo integrated with QuickCheck.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Hspec}
\label{sec:hspec}

TBD.

@@

\noindent We should execute {\tt doctest} to ensure no syntax errors.
Also, we specifies internal behaviors with {\tt Hspec}:

@@

\noindent Also, we should execute this Hspec module
to ensure no syntax errors.
Then we implement the function.

@@

A driver for Hspec looks like so:

>>>>

\authorinfo{Simon HENGEL}
           {TBD: Affiliation}
           {TBD: Email}
%% \authorinfo{Trystan SPANGLER}
%%            {TBD: Affiliation}
%%            {TBD: Email}
\authorinfo{Kazuhiko YAMAMOTO}
           {IIJ Innovation Institute Inc.}
           {kazu@iij.ad.jp}

@@

In this paper, we explore how to apply BDD to Haskell.
We brought a test method from other programming language community and
integrated it with a Haskell-original test method.
In particular, we introduced {\tt doctest}~\cite{doctest} and
integrated with QuickCheck~\cite{quickcheck} as a BDD tool.
We also make use of \hspec{} inspired by rspec~\cite{rspec}.

@@

\begin{itemize}
\item Introduced {\tt doctest} from Python community to Haskell community
and integrated it with QuickCheck
(Section \ref{sec:Visible-behavior} and Section \ref{sec:doctest})
%% \item Introduced {\tt Hspec} from Ruby community to Haskell community and
%% integrated it with QuickCheck
%% (Section \ref{sec:Internal-behavior} and Section \ref{sec:hspec})
\item Show best current practice of behavior driven development in Haskell using {\tt doctest} and \hspec{} (Section \ref{ref:Best-current-practice})
\end{itemize}

@@

In Haskell community, HUnit and QuickCheck are commonly used %% what about SmallCheck?
and the {\tt test-framework} package integrates them.
We can categorize the {\tt test-framework} package into
a tool of TDD.
Before our work and \hspec{}, there is no BDD tool commonly used in Haskell community.

@@

To specify visible behavior, we propose to add two new annotation syntax to Haddock and to use {\tt doctest} integrated with QuickCheck. To describe internal behavior, we propose to use \hspec{} aslo integrated with QuickCheck.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \subsection{Hspec}
%% \label{sec:hspec}

%% TBD.

@@

\noindent We should execute {\tt doctest} to ensure no syntax errors.
Also, we specifies internal behaviors with \hspec{}:

@@

\noindent Also, we should execute this \hspec{} module
to ensure no syntax errors.
Then we implement the function.

@@

A driver for \hspec{} looks like so:
